\bf Calendar-based graphics for visualizing people's daily schedules

### 2019-04-03 reviews/response.Rmd

Done.

> p25, l14: "Anzac Day in Australia, or Thanksgiving Day in the USA,": Never mentioned before in this article. Refer back to the special events/holidays from earlier in the article.

ToDo.

> p25, after l35: List my suggestions for software additions from above that you do not want to implement now as options for future work.

> Fig.16 caption: "Calendar display for household 1, indicates higher weekend usage, and in the summer months, November-February. It seems that they took a vacation in June." ->
"The calendar display for household 1 indicates higher weekend usage and higher usage in the summer months (November-February). It seems that this household took a vacation in June."

> Fig.17 caption: "Calendar display for household 2, reveals their tendency to use air conditioning and heating continuously. Not many vacation were taken." ->
"The calendar display for household 2 reveals their tendency to use air conditioning
and heating continuously. Some vacation days were taken in late December and in the
second week of June."

> Fig.17: I am concerned: Is this a "fair" comparison when you drop the months August-October (& part of November) 2017 for household 2, while these 3+ months
are part of the graphics for households 1, 3 & 4? Wouldn't it be better to
restrict all households to Dec 2017 - July 2018? This would drop the winter/spring months from the aggregated displays in Figs.14-15. But household 2 still would have most variation, but now, this is based on matching time periods.

> Fig.18 caption: "Calendar display for household 3. Their energy use reveals higher energy use in
the winter months, with multiple peaks daily on both week days and weekends. There are some high peaks in summer, perhaps indicating occasional air conditioner use. There have been several long vacations in the past year." ->
"The calendar display for household 3 reveals higher energy use in
the winter months (May-August), with multiple peaks daily on both week days and weekends. There are
some high peaks in summer (November-February), perhaps indicating occasional air conditioner use. There have
been several long vacations ... [match the main text]."

> Fig.19 caption: "Calendar display for household 4, shows energy use mostly in the evenings and on weekends. Three short trips were taken in October, December, and June." ->
"The calendar display for household 4 shows energy use mostly in the evenings and
on weekends. Three short trips were taken in October, December, and June." [also April? - match with p25, l13]

> p.30: City of Melbourne (2017) [& other URLs]: Does JCGS require the "last accessed" information for web-based references? If so, add where needed.

### 2019-04-03 main.Rmd
done with misc stuff

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE, 
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = TRUE, external = TRUE, out.width = "\\textwidth"
)
read_chunk('src/main.R')
```

@@

Figure \@ref(fig:h1)-\@ref(fig:h4) display the data in calendar layout individually for each household, unfolding their day-to-day life. Glancing over household 1, we can see that their overall energy use is low. Their week day energy use is distinguishable from their weekends, indicating a working household. The air conditioner appears to be used in the summer months (December--February) in the evening and weekends. In household 2, heating keeps functioning for consecutive hours, which is evident in the mid July. In contrast, household 1 uses heating cautiously. These observations help to explain the stripes and clusters in Figure \@ref(fig:hod). The calendar plots speak the stories about vacation time that are untold by previous plots. Household 1 is on vacation over three weeks of June, and household 2 was also away for vacation in late December and in the second week of June. Figure \@ref(fig:h3) shows household 3 takes two one-month-long family trips in September until early October and in June/July. Household 4 is away over two or three weeks in early October, December, early April, and late June. The use of air conditioning and heating leaves no trace in these two households.

```{r h1, fig.height = 7, fig.cap = "Calendar display for household 1, indicates higher weekend usage, and in the summer months, November-February. It seems that they took a vacation in June."}
```

```{r h2, fig.height = 7, fig.cap = "Calendar display for household 2, reveals their tendency to use air conditioning and heating continuously. Not many vacation were taken."}
```

```{r h3, fig.height = 7, fig.cap = "Calendar display for household 3. Their energy use reveals higher energy use in the winter months, with multiple peaks daily on both week days and weekends. There are some high peaks in summer, perhaps indicating occasional air conditioner use. There have been several long vacations in the past year."}
```

```{r h4, fig.height = 7, fig.cap = "Calendar display for household 4, shows energy use mostly in the evenings and on weekends. Four short trips were taken in October, December, April, and June."}
```

>>>>

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE, 
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = FALSE, external = TRUE,
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
read_chunk('src/main.R')
```

@@

Figure \@ref(fig:h1)-\@ref(fig:h4) display the data in calendar layout individually for each household, unfolding their day-to-day life. Glancing over household 1, we can see that their overall energy use is low. Their week day energy use is distinguishable from their weekends, indicating a working household. The air conditioner appears to be used in the summer months (November-February) in the evening and weekends. In household 2, heating keeps functioning for consecutive hours, which is evident in the mid July. In contrast, household 1 uses heating cautiously. These observations help to explain the stripes and clusters in Figure \@ref(fig:hod). The calendar plots speak the stories about vacation time that are untold by previous plots. Household 1 is on vacation over three weeks of June, and household 2 was also away for vacation in late December and in the second week of June. Figure \@ref(fig:h3) shows household 3 takes two one-month-long family trips in September until early October and in June/July. Household 4 is away over two or three weeks in early October, December, early April, and late June. The use of air conditioning and heating leaves no trace in these two households.

```{r h1, fig.height = 7, fig.cap = "The calendar display for household 1 indicates higher weekend usage and higher usage in the summer months (November-February). It seems that this household took a vacation in June."}
```

```{r h2, fig.height = 7, fig.cap = "The calendar display for household 2 reveals their tendency to use air conditioning and heating continuously. Some vacation days were taken in late December and in the second week of June."}
```

```{r h3, fig.height = 7, fig.cap = "The calendar display for household 3 reveals higher energy use in the winter months (May-August), with multiple peaks daily on both week days and weekends. There are some high peaks in summer (November-February), perhaps indicating occasional air conditioner use. There have been several long vacations in the past year."}
```

```{r h4, fig.height = 7, fig.cap = "The calendar display for household 4 shows energy use mostly in the evenings and on weekends. Four short trips were taken in October, December, April, and June."}
```

### 2019-04-03 main.tex
used bookdown::pdf_book
added DESCRIPTION file
done with misc stuff

\begin{equation}
  \begin{aligned}
  i &= \lceil (g \text{ mod } 35) / 7\rceil, \\
  j &= g \text{ mod } 7. \label{eq:grid}
  \end{aligned}
\end{equation}

@@

\begin{equation}
  \begin{aligned}
  x &= j + (n - 1) \times 7 + (n - 1) \times b + h, \\
  y &= i - (m - 1) \times 5 - (m - 1) \times b + c. \label{eq:final}
  \end{aligned}
\end{equation}

@@

Figure \ref{fig:h1}-\ref{fig:h4} display the data in calendar layout individually for each household, unfolding their day-to-day life. Glancing over household 1, we can see that their overall energy use is low. Their week day energy use is distinguishable from their weekends, indicating a working household. The air conditioner appears to be used in the summer months (December--February) in the evening and weekends. In household 2, heating keeps functioning for consecutive hours, which is evident in the mid July. In contrast, household 1 uses heating cautiously. These observations help to explain the stripes and clusters in Figure \ref{fig:hod}. The calendar plots speak the stories about vacation time that are untold by previous plots. Household 1 is on vacation over three weeks of June, and household 2 was also away for vacation in late December and in the second week of June. Figure \ref{fig:h3} shows household 3 takes two one-month-long family trips in September until early October and in June/July. Household 4 is away over two or three weeks in early October, December, early April, and late June. The use of air conditioning and heating leaves no trace in these two households.

@@

\caption{Calendar display for household 1, indicates higher weekend usage, and in the summer months, November-February. It seems that they took a vacation in June.}\label{fig:h1}
\end{figure}

@@

\caption{Calendar display for household 2, reveals their tendency to use air conditioning and heating continuously. Not many vacation were taken.}\label{fig:h2}
\end{figure}

@@

\caption{Calendar display for household 3. Their energy use reveals higher energy use in the winter months, with multiple peaks daily on both week days and weekends. There are some high peaks in summer, perhaps indicating occasional air conditioner use. There have been several long vacations in the past year.}\label{fig:h3}
\end{figure}

@@

\caption{Calendar display for household 4, shows energy use mostly in the evenings and on weekends. Three short trips were taken in October, December, April, and June.}\label{fig:h4}
\end{figure}

>>>>

\begin{equation}
  \begin{aligned}
  i &= \lceil (g \text{ mod } 35) / 7\rceil, \\
  j &= g \text{ mod } 7.
  \end{aligned}
  \label{eq:grid}
\end{equation}

@@

\begin{equation}
  \begin{aligned}
  x &= j + (n - 1) \times 7 + (n - 1) \times b + h, \\
  y &= i - (m - 1) \times 5 - (m - 1) \times b + c.
  \end{aligned}
  \label{eq:final}
\end{equation}

@@

Figure \ref{fig:h1}-\ref{fig:h4} display the data in calendar layout individually for each household, unfolding their day-to-day life. Glancing over household 1, we can see that their overall energy use is low. Their week day energy use is distinguishable from their weekends, indicating a working household. The air conditioner appears to be used in the summer months (November-February) in the evening and weekends. In household 2, heating keeps functioning for consecutive hours, which is evident in the mid July. In contrast, household 1 uses heating cautiously. These observations help to explain the stripes and clusters in Figure \ref{fig:hod}. The calendar plots speak the stories about vacation time that are untold by previous plots. Household 1 is on vacation over three weeks of June, and household 2 was also away for vacation in late December and in the second week of June. Figure \ref{fig:h3} shows household 3 takes two one-month-long family trips in September until early October and in June/July. Household 4 is away over two or three weeks in early October, December, early April, and late June. The use of air conditioning and heating leaves no trace in these two households.

@@

\caption{The calendar display for household 1 indicates higher weekend usage and higher usage in the summer months (November-February). It seems that this household took a vacation in June.}\label{fig:h1}
\end{figure}

@@

\caption{The calendar display for household 2 reveals their tendency to use air conditioning and heating continuously. Some vacation days were taken in late December and in the second week of June.}\label{fig:h2}
\end{figure}

@@

\caption{The calendar display for household 3 reveals higher energy use in the winter months (May-August), with multiple peaks daily on both week days and weekends. There are some high peaks in summer (November-February), perhaps indicating occasional air conditioner use. There have been several long vacations in the past year.}\label{fig:h3}
\end{figure}

@@

\caption{The calendar display for household 4 shows energy use mostly in the evenings and on weekends. Four short trips were taken in October, December, April, and June.}\label{fig:h4}
\end{figure}
